Software Frameworks for Parallel Deep Learning

### 2016-07-28 report/Report/para/0-abstract.tex
changed title, editted intro and abstract

\begin{abstract}
The study and adoption of deep learning methods has led to significant progress in different application domains. As deep learning continues to show promise and its utilization matures, so does the infrastructure and software needed to support it. Various frameworks have been developed in recent years to facilitate both implementation and training of deep learning networks. As deep learning has also evolved to becoming distributed, there's a growing need for frameworks that can support execution across multiple machines. While deep learning frameworks restricted to running on a single machine have been studied and compared, frameworks which support distributed deep learning are relatively less known and well-studied. This paper seeks to bridge that gap by surveying, summarizing, and comparing frameworks which currently support distributed execution, including but not limited to Tensorflow, CNTK, Deeplearning4j, MXNet, H2O, and CaffeOnSpark.
\end{abstract}

>>>>

\begin{abstract}
The study and adoption of deep learning methods has led to significant progress in different application domains. As deep learning continues to show promise and its utilization matures, so does the infrastructure and software needed to support it. Various frameworks have been developed in recent years to facilitate both implementation and training of deep learning networks. As deep learning has also evolved to scale across multiple machines, there's a growing need for frameworks that can provide full parallel support. While deep learning frameworks restricted to running on a single machine have been studied and compared, frameworks which support parallel deep learning at scale are relatively less known and well-studied. This paper seeks to bridge that gap by surveying, summarizing, and comparing frameworks which currently support distributed execution, including but not limited to Tensorflow, CNTK, Deeplearning4j, MXNet, H2O, CaffeOnSpark, Theano, and Torch. 
\end{abstract}

### 2016-07-28 report/Report/para/1-introduction.tex
changed title, editted intro and abstract

The goal of this paper is to survey the landscape of deep learning frameworks with distributed execution, and compare them across a consistent set of characteristics. These characteristics include release date, core language, user-facing API, computation model, communication model, data parallelism, model parallelism, programming paradigm, fault tolerance, and visualization. This choice of criteria is explained in detail in Section 2. Tensorflow, CNTK, Deeplearning4j, MXNet, H2O, and CaffeOnSpark were chosen by a combination of factors, including their being open-source, level of documentation, maturity as a product, and adoption by the community. These frameworks are examined in detail in Section 3. Additional frameworks without built-in distributed support, such as Theano, Torch, and native Caffe, are mentioned alongside known external distributed implementations. Finally, the nuances of the relationship between training scalability and problem size is discussed, in the context of distributed frameworks, also in Section 3. Section 4 concludes the paper.

>>>>

The goal of this paper is to survey the landscape of deep learning frameworks with full support for parallelization. Three levels of parallelization exist on the hardware level: within a GPU, between GPUs on a single node, and between nodes. Two forms of parallelism also exist on the application level: model and data parallelism. Other aspects of frameworks include release date, core language, user-facing API, computation model, communication model, programming paradigm, fault tolerance, and visualization. This choice of criteria is explained in detail in Section 2. Tensorflow, CNTK, Deeplearning4j, MXNet, H2O, CaffeOnSpark, Theano, and Torch do not necessarily encompass the entire space of frameworks for deep learning. However, these were chosen by a combination of factors, including their being open-source, level of documentation, maturity as a complete product, and level of adoption by the community. These frameworks, as well as some others not included in the Section 2 chart, are examined in detail in Section 3. Additional comments regarding parallelism in deep learning, as well as scalability, are also discussed at the end of Section 3. Section 4 concludes the paper.
